%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5} 
\usepackage[scale=0.90,lf]{FiraMono}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in} % Tighter top margin
\addtolength{\textheight}{1.2in} % Tighter bottom margin

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large \uppercase 
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}} % Tighter bullet spacing
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ 
      \textit{#3} & {\color{dark-grey} \small #4}\\ 
    \end{tabular*}\vspace{-6pt} % Tighter subheading spacing
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\color{text-grey}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Prakhar Chandrakar} \\ \vspace{4pt}
    \small \faPhone* \texttt{+91 9406052751} \hspace{2pt} $|$ \hspace{2pt}
    \faEnvelope \hspace{2pt} \href{mailto:prakhar3823@gmail.com}{\texttt{prakhar3823@gmail.com}} \\ \vspace{2pt}
    \faGlobe \hspace{2pt} \href{https://prakhar383.github.io/My-portfolio/}{\texttt{prakhar383.github.io/My-portfolio}} \hspace{2pt} $|$ \hspace{2pt}
    \faGithub \hspace{2pt} \href{https://github.com/prakhar383}{\texttt{github.com/prakhar383}} \hspace{2pt} $|$ \hspace{2pt}
    \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/prakhar-chandrakar-2405b93b3/}{\texttt{linkedin.com/in/prakhar-chandrakar}}
    \\ \vspace{-4pt}
\end{center} 

%-----------PROFESSIONAL SUMMARY-----------
\section{Summary}
\vspace{1pt}
\small{AI Engineer specializing in end-to-end LLM orchestration, RAG architectures, and multi-agent systems via LangChain and LangGraph. Dedicated to deploying scalable, high-accuracy AI solutions with high-performance Python backends and MLOps best practices.}
\vspace{2pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B.Tech in Computer Science (AI) | CPI: 7.14}{2021 -- 2025}
      {Chhattisgarh Swami Vivekananda Technical University}{Bhilai, C.G.}
    \resumeSubheading
      {CBSE Science | Percentage: 82.00\%}{2020 -- 2021}
      {Krishna Public School}{Bhilai, C.G.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Computer Vision Research Intern}{}
      {International Institute of Information Technology (IIIT)}{Naya Raipur, C.G.}
      \resumeItemListStart
        \resumeItem{Engineered and trained custom YOLOv8 model achieving \textbf{93\% detection accuracy} with curated dataset of 20,000+ annotated images.}
        \resumeItem{Optimized real-time video processing pipeline using OpenCV, reducing frame inference latency by \textbf{30\%} through parameter tuning.}
        \resumeItem{Built end-to-end Python pipeline integrating face recognition, NumPy, and text-to-speech (Pyttsx3) for automated processing workflow.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, SQL, HTML/CSS, PHP} \\
     \textbf{Frontend}{: React, Next.js, Streamlit} \\
     \textbf{Backend}{: Node.js, FastAPI, Django, Express.js} \\
     \textbf{Databases}{: MongoDB, PostgreSQL, MySQL} \\
     \textbf{AI/ML}{: YOLOv8, OpenCV, LangChain, LangGraph, NumPy, Pandas, Scikit-learn} \\
     \textbf{Tools}{: REST APIs, Git/GitHub, Groq API, Gemini API, Docker}
    }}
 \end{itemize}
 \vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
\resumeProjectHeading
  {\href{https://github.com/prakhar383/AI-JD-Analyzer-and-Resume-Maker}{\texteb{AI-JD-Analyzer-and-Resume-Maker}} $|$ \emph{Python, FastAPI, Groq API, LaTeX}}{}
  \resumeItemListStart
    \resumeItem{Engineered an automated ATS-optimized LaTeX resume generator that intelligently aligns candidate profile data with specific job requirements.}
    \resumeItem{Utilized custom prompt engineering and multi-agent LLM scoring to achieve dynamic PDF generation and high-confidence keyword injection.}
  \resumeItemListEnd

\resumeProjectHeading
  {\href{https://github.com/prakhar383/Ai-Chat-Based-Database-Manager}{\texteb{Ai-Chat-Based-Database-Manager}} $|$ \emph{LangGraph, Llama-3, FastAPI, PostgreSQL, React}}{}
  \resumeItemListStart
    \resumeItem{Developed a Human-in-the-Loop CRM module allowing seamless database interaction and HCP logging via autonomous natural language chat.}
    \resumeItem{Orchestrated a stateful LangGraph agent to handle multi-tool data extraction and secure PostgreSQL record generation from raw chat input.}
  \resumeItemListEnd

\resumeProjectHeading
  {\href{https://github.com/prakhar383/Minutes-of-Meeting-Generator.}{\texteb{Minutes-of-Meeting-Generator.}} $|$ \emph{Deepgram Nova-2, Llama-3.1, Python, RAG}}{}
  \resumeItemListStart
    \resumeItem{Revolutionized documentation workflows by transforming raw meeting recordings into structured, decision-oriented summaries automatically.}
    \resumeItem{Integrated Deepgram's Nova-2 model for transcription with Llama-3.1 for summarization within a containerized RAG-optimized environment.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd
 
%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeItemListStart
    \resumeItem{\texteb{High Performance Scientific Computing} (NPTEL, 2025) \hspace{1pt} $|$ \hspace{1pt} \texteb{Data Structures \& Algorithms} (Learn and Build, 2023)}
\resumeItemListEnd

\end{document}
